---
title: "archive_sentiment"
author: "Julianna Alvord"
date: "3/15/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(rtweet)
library(rvest)
library(magrittr)
library(tidyr)
library(stringr)
library(ggplot2)
library(tidytext)
```

#loading the data
```{r}
#loading starters data
subset2 <- read.csv("/Users/juliannaalvord/Documents/nfl sentiment/final_data/subset2.csv", stringsAsFactors = FALSE)

#loading tweets file from archive_cleaning
load("/Users/juliannaalvord/Documents/nfl sentiment/final_data/archive_tweets_final.rda")

#loading outcomes
outcomes <- read.csv("/Users/juliannaalvord/Documents/nfl sentiment/final_data/outcomes.csv", stringsAsFactors = F)
```

#adding some sentiments to bing lexicon
```{r}
#creating data frame with additional sentiments
extra<-data.frame(c("rings", "ring", "history", "clutch", "congrats", "dynasty", "goat", "g.o.a.t."), 
               c("positive", "positive", "positive", "positive", "positive", "positive", "positive", "positive"))
names(extra) <- c("word", "sentiment")

#binding to bing lexicon
bing_lex <- get_sentiments("bing")

sent_full <- rbind(bing_lex, extra)
```

#running loop to get sentiments
```{r}
#list of names for loop
names <- as.list(subset2$name_clean)

#empty list to add sentiments for each player
datalist = list()

for(i in 1:24) {
  
  #filter for each person
  tweets <- tweets_final %>%
    filter(name_clean_final == names[i])
  
  #pick out words
  words <- tweets %>% 
    select(ID, full_text_low) %>% 
    unnest_tokens(word,full_text_low)
  
  #creating df of stop words  
  my_stop_words <- stop_words %>% 
    select(-lexicon) %>% 
    bind_rows(data.frame(word = c("https", "t.co", "rt", "amp","4yig9gzh5t","fyy2ceydhi","78","fakenews")))

  #anti-join with stop words to filter those words out
  tweet_words <- words %>% 
    anti_join(my_stop_words)

  #joining sentiments with non-stop words from tweets
  fn_sentiment <- tweet_words %>% 
    left_join(sent_full) 
  
  #creating df with n of sentiments
  df <- fn_sentiment %>% 
    filter(!is.na(sentiment)) %>% 
    group_by(sentiment) %>% 
    summarise(n=n())

  #making df of sentiments for each person
  df_2 <- df %>%
  mutate(player = names[i]) %>%
  spread(key = sentiment, value = n)
  
  datalist[[i]] <- df_2
  
  
  
  ######uncomment next part if you want words df or sentiments dfs to be loaded into environment
  
  
  
  #creating name for dfs
  #df_name <- name
  
  #words_name <- paste(name, "word", sep = "_")

  #assigning df_name to df
  #assign(df_name, df_2)
  
}

#sentiments n for all players
sentiments_full_bing = do.call(rbind, datalist)
```


#Joining with starter data
```{r}
sentiments_full_bing2 <- sentiments_full_bing %>%
  mutate(player = as.character(player))

#creating percentages
subset_sentiment <- subset2 %>%
  left_join(sentiments_full_bing2, by = c("name_clean" = "player")) %>%
  mutate(totalsentiment = positive+negative,
         neg_perc = negative/totalsentiment * 100,
         pos_perc = positive/totalsentiment *100)


#gathering by race, player, and sentiment
subset_sent_format <- subset_sentiment %>%
  select(name_clean, Race, 19:20) %>%
  gather(sentiment, n, 3:4)

#grouping by sentiment and race then making mean for each sentiment/race
subset_sent_2 <- subset_sent_format %>%
  dplyr::group_by(sentiment, Race) %>%
  summarise(mean_perc_sent = mean(n))

#sentiments by race
ggplot(subset_sent_2, aes(x = sentiment, y = mean_perc_sent, fill = Race)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_manual(values=c("black", "white"))
```

#adding in position
```{r}
qb <- c("alex smith", "jameis winston", "joe flacco", "carson wentz", "cam newton", 
        "dak prescott", "russell wilson", "andy dalton")

#adding in position
subset_sentiment <- subset_sentiment %>%
  mutate(position = ifelse(name_clean %in% qb, "qb", "r"))

#gathering by race, player and sentiment
subset_sent_format <- subset_sentiment %>%
  select(name_clean, Race, position, 19:20) %>%
  gather(sentiment, n, 4:5)

#grouping by sentiment and race then making mean for each sentiment/race
subset_sent_2 <- subset_sent_format %>%
  dplyr::group_by(sentiment, Race, position) %>%
  summarise(mean_perc_sent = mean(n))

#same viz but by position as well
ggplot(subset_sent_2, aes(x = sentiment, y = mean_perc_sent, fill = Race)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_manual(values=c("black", "white")) + facet_wrap(~position, ncol = 1)
```

#Need to rerun sentiments depending on time -- writing function
```{r}
sent <- function(t){
  
names <- as.list(subset2$name_clean)

datalist = list()

for(i in 1:24) {
  
  
  #filter for each person and the correct time
  tweets <- tweets_final %>%
    filter(name_clean_final == names[i],
           time == paste0("t_", t))
  
  #pick out words
  words <- tweets %>% 
    select(ID, full_text_low) %>% 
    unnest_tokens(word,full_text_low)
  
  #creating df of stop words  
  my_stop_words <- stop_words %>% 
    select(-lexicon) %>% 
    bind_rows(data.frame(word = c("https", "t.co", "rt", "amp","4yig9gzh5t","fyy2ceydhi","78","fakenews")))

  #anti-join with stop words to filter those words out
  tweet_words <- words %>% 
    anti_join(my_stop_words)

  #joining sentiments with non-stop words from tweets
  fn_sentiment <- tweet_words %>% 
    left_join(sent_full) 
  
  #creating df with n of sentiments
  df <- fn_sentiment %>% 
    filter(!is.na(sentiment)) %>% 
    group_by(sentiment) %>% 
    summarise(n=n())

  #making df of sentiments for each person
  df_2 <- df %>%
  mutate(player = names[i]) %>%
  spread(key = sentiment, value = n)
  
  datalist[[i]] <- df_2
  
  
  
  ######uncomment next part if you want words df or sentiments dfs to be loaded into environment
  
  
  
  #creating name for dfs
  #df_name <- name
  
  #words_name <- paste(name, "word", sep = "_")

  #assigning df_name to df
  #assign(df_name, df_2)
  
}
  
#return(datalist)


sentiment_full <- do.call(bind_rows, datalist)

sentiment_full <- sentiment_full %>%
  mutate(totalsentiment = negative + positive,
         neg_perc = negative/totalsentiment * 100,
         pos_perc = positive/totalsentiment *100,
         time = paste0("t_", t),
         player = as.character(player)) %>%
  plyr::rename(c("negative" = paste0("negative", t),
         "positive" = paste0("positive", t),
         "totalsentiment" = paste0("totalsentiment", t),
         "neg_perc" = paste0("neg_perc", t),
         "pos_perc" = paste0("pos_perc", t)))
  

return(sentiment_full)

}
```


#running the function to get sentiments for all the times
```{r}
#sentiments for time 1
sent_1 <- sent(1)

#sentiment for time 2
sent_2 <- sent(2)

#sentiment for time 3
sent_3 <- sent(3)

#sentiment for time 4
sent_4 <- sent(4)

#sentiment for time 5
sent_5 <- sent(5)

#combining outcome to players
outcomes_players <- subset2 %>%
  full_join(outcomes, by = "Team")

#joining all the sentiments to the subset 
subset_full <- subset2 %>%
  left_join(sent_1, by = c("name_clean" = "player")) %>%
  left_join(sent_2, by = c("name_clean" = "player")) %>%
  left_join(sent_3, by = c("name_clean" = "player")) %>%
  left_join(sent_4, by = c("name_clean" = "player")) %>%
  left_join(sent_5, by = c("name_clean" = "player"))

#(above is long dataset)
```

#new function to create tall dataset
```{r}
sent_tall <- function(t){
  
names <- as.list(subset2$name_clean)

datalist = list()

for(i in 1:24) {
  
  
  #filter for each person and the correct time
  tweets <- tweets_final %>%
    filter(name_clean_final == names[i],
           time == paste0("t_", t))
  
  #pick out words
  words <- tweets %>% 
    select(ID, full_text_low) %>% 
    unnest_tokens(word,full_text_low)
  
  #creating df of stop words  
  my_stop_words <- stop_words %>% 
    select(-lexicon) %>% 
    bind_rows(data.frame(word = c("https", "t.co", "rt", "amp","4yig9gzh5t","fyy2ceydhi","78","fakenews")))

  #anti-join with stop words to filter those words out
  tweet_words <- words %>% 
    anti_join(my_stop_words)

  #joining sentiments with non-stop words from tweets
  fn_sentiment <- tweet_words %>% 
    left_join(sent_full) 
  
  #creating df with n of sentiments
  df <- fn_sentiment %>% 
    filter(!is.na(sentiment)) %>% 
    group_by(sentiment) %>% 
    summarise(n=n())

  #making df of sentiments for each person
  df_2 <- df %>%
  mutate(player = names[i]) %>%
  spread(key = sentiment, value = n)
  
  datalist[[i]] <- df_2
  
  
  
  ######uncomment next part if you want words df or sentiments dfs to be loaded into environment
  
  
  
  #creating name for dfs
  #df_name <- name
  
  #words_name <- paste(name, "word", sep = "_")

  #assigning df_name to df
  #assign(df_name, df_2)
  
}
  
#return(datalist)


sentiment_full <- do.call(bind_rows, datalist)

sentiment_full <- sentiment_full %>%
  mutate(totalsentiment = negative + positive,
         neg_perc = negative/totalsentiment * 100,
         pos_perc = positive/totalsentiment *100,
         time = paste0("t_", t),
         player = as.character(player))
  # plyr::rename(c("negative" = paste0("negative", t),
  #        "positive" = paste0("positive", t),
  #        "totalsentiment" = paste0("totalsentiment", t),
  #        "neg_perc" = paste0("neg_perc", t),
  #        "pos_perc" = paste0("pos_perc", t)))
  

return(sentiment_full)

}
```

#running new function then creating tall dataset
```{r}
#sentiments for time 1
sent_tall_1 <- sent_tall(1)

#sentiment for time 2
sent_tall_2 <- sent_tall(2)

#sentiment for time 3
sent_tall_3 <- sent_tall(3)

#sentiment for time 4
sent_tall_4 <- sent_tall(4)

#sentiment for time 5
sent_tall_5 <- sent_tall(5)

#combining outcome to players
outcomes_players <- subset2 %>%
  full_join(outcomes, by = "Team")



#row_binding all of the sentiments together

sent_tall_full <- sent_tall_1 %>%
  bind_rows(sent_tall_2, sent_tall_3, sent_tall_4, sent_tall_5)



#joining sentiment tall to outcomes
sent_tall_full1 <- outcomes_players %>%
  left_join(sent_tall_full, by = c("name_clean" = "player", "time"))
```

#Yay! Now I can use outcome
```{r}

sent_tall_full1$outcome1 <- factor(sent_tall_full1$outcome, labels = c("Lost", "Won"))

#gathering by race, player and sentiment
subset_sent_format <- sent_tall_full1 %>%
  select(name_clean, Race, outcome1, 21:22) %>%
  gather(sentiment, n, 4:5)

#grouping by sentiment and race then making mean for each sentiment/race
subset_sent_2 <- subset_sent_format %>%
  dplyr::group_by(sentiment, Race, outcome1) %>%
  summarise(mean_perc_sent = mean(n, na.rm = T))

subset_sent_2 <- subset_sent_2 %>%
  filter(sentiment == "neg_perc")

#same viz but by outcome as well
ggplot(subset_sent_2, aes(x = sentiment, y = mean_perc_sent, fill = Race)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_manual(values=c("black", "white")) + facet_wrap(~outcome1) +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  xlab("Percentage of Negative Words") +
  ylab("Average Percentage of Total Sentiment") +
  geom_text(
    aes(label = round(mean_perc_sent, digits = 2), y = mean_perc_sent + 1),
    position = position_dodge(0.9),
    vjust = 0
  )
```


#outcome and position
```{r}
qb <- c("alex smith", "jameis winston", "joe flacco", "carson wentz", "cam newton", 
        "dak prescott", "russell wilson", "andy dalton")

sent_tall_full1$outcome1 <- factor(sent_tall_full1$outcome, labels = c("Lost", "Won"))

#adding in position
sent_tall_full1 <- sent_tall_full1 %>%
  mutate(position = ifelse(name_clean %in% qb, "Quarterback", "Receiver"))

#gathering by race, player and sentiment
subset_sent_format <- sent_tall_full1 %>%
  select(name_clean, Race, outcome1, position, 21:22) %>%
  gather(sentiment, n, 5:6)

#grouping by sentiment and race then making mean for each sentiment/race
subset_sent_2 <- subset_sent_format %>%
  dplyr::group_by(sentiment, Race, outcome1, position) %>%
  summarise(mean_perc_sent = mean(n, na.rm = T))

#getting rid of positive perc
subset_sent_2 <- subset_sent_2 %>%
  filter(sentiment == "neg_perc")

#same viz but by outcome as well
ggplot(subset_sent_2, aes(x = sentiment, y = mean_perc_sent, fill = Race)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_manual(values=c("black", "white")) + facet_grid(position ~ outcome1) +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  xlab("Percentage of Negative Words") +
  ylab("Average Percentage of Total Sentiment") +
  geom_text(
    aes(label = round(mean_perc_sent, digits = 2), y = mean_perc_sent + 1),
    position = position_dodge(0.9),
    vjust = 0
  )
```


